DATA 624 Homework 5

### 2020-03-06 DATA624/HW5.Rmd
More work on HW5

@@

```{r}
retaildata <- read_excel("retail.xlsx", skip = 1)
retail_ts <- ts(retaildata[, "A3349873A"], frequency = 12, start = c(1982, 4))

hw_multiplicative <- hw(retail_ts, seasonal = "multiplicative")
autoplot(hw_multiplicative) + 
  ggtitle("Multiplicative") + 
  ylab("Retail Sales")

hw_multiplicative_damped <- hw(retail_ts, seasonal = "multiplicative", damped = TRUE)
autoplot(hw_multiplicative_damped) + 
  ggtitle("Multiplicative & Damped") + 
  ylab("Retail Sales")
```

@@

@@

@@

>>>>

**As we have seen in the previous sections, the variability in the series is increasing over time.  This calls for a method that accounts for multiplicative seasonality.  Here's the plot in case you have forgotten what the time series looks like:**

```{r}
retaildata <- read_excel("retail.xlsx", skip = 1)
retail_ts <- ts(retaildata[, "A3349873A"], frequency = 12, start = c(1982, 4))
autoplot(retail_ts) + ylab("Retail Sales")
```

@@

```{r}
hw_multiplicative <- hw(retail_ts, seasonal = "multiplicative")
autoplot(hw_multiplicative) + 
  ggtitle("Multiplicative") + 
  ylab("Retail Sales")
summary(hw_multiplicative)

hw_multiplicative_damped <- hw(retail_ts, seasonal = "multiplicative", damped = TRUE)
autoplot(hw_multiplicative_damped) + 
  ggtitle("Multiplicative & Damped") + 
  ylab("Retail Sales")
summary(hw_multiplicative_damped)
```

@@

```{r}
cat("RMSE of Multiplicative = ", accuracy(hw_multiplicative)[2])
```

```{r}
cat("RMSE of Multiplicative & Damped = ", accuracy(hw_multiplicative_damped)[2])
```

**The non-damped model is preforming better.**

@@

```{r}
checkresiduals(hw_multiplicative)
```

**The residuals looks like white noise to me.  They are normally distributed with a mean of zero, with no pattern over time.**

@@

```{r}
retail_train <- window(retail_ts, end = c(2010, 12))
retail_test <- window(retail_ts, start = 2011)

get_retail_test_rmse <- function(model){
  accuracy(model, retail_test)[4]
}

Model <- c("Seasonal Naïve (Baseline)", 
           "SES",
           "Holt's Method",
           "Damped Holt's Method",
           "Holt-Winters Additive",
           "Holt-Winters Multiplicative",
           "Damped Holt-Winters Additive",
           "Damped Holt-Winters Multiplicative")

RMSE <- c(get_retail_test_rmse(snaive(retail_train)), 
          get_retail_test_rmse(ses(retail_train)),
          get_retail_test_rmse(holt(retail_train)),
          get_retail_test_rmse(holt(retail_train, damped = TRUE)),
          get_retail_test_rmse(hw(retail_train, seasonal = "additive")),
          get_retail_test_rmse(hw(retail_train, seasonal = "multiplicative")),
          get_retail_test_rmse(hw(retail_train, seasonal = "additive", damped = TRUE)),
          get_retail_test_rmse(hw(retail_train, seasonal = "multiplicative", damped = TRUE)))

rmse_df <- data.frame(Model, RMSE)

rmse_df %>%
  kable() %>%
  kable_styling()
```

**This was and interesting exercise.  Some of the more sophisticated approaches preformed less well on the test set than the seasonal naïve model.  In the end the `r rmse_df[rmse_df$RMSE == min(rmse_df$RMSE),]$Model` preformed the best on the test set.**
